---
output:
  md_document:
    variant: markdown_github
---
### domaintools - an R API interface to the DomainTools API

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

The following functions are implemented:

- `domaintools_api_key`:	Get or set DOMAINTOOLS_API_KEY value
- `domaintools_username`:	Get or set DOMAINTOOLS_API_USERNAME value
- `domain_profile`:	Domain Profile
- `hosting_history`:	Hosting History
- `parsed_whois`:	Parsed Whois
- `reverse_ip`:	Reverse IP
- `reverse_ns`:	Reverse Nameserver
- `shared_ips`:	Shared IPs
- `whois`:	Whois Lookup
- `whois_history`:	Whois History

### News

- Version 0.0.1.9000 : Bugfixes contributed by David Severski
- Version 0.0.0.9000 released

### Installation

```{r eval=FALSE}
devtools::install_github("hrbrmstr/domaintools")
```

```{r echo=FALSE, message=FALSE, warning=FALSE, error=FALSE}
options(width=120)
```

### Usage

```{r}
library(domaintools)

# current verison
packageVersion("domaintools")

whois("domaintools.com")

whois_history("domaintools.com")

domain_profile("domaintools.com")

hosting_history("domaintools.com")

```

### Test Results

```{r}
library(domaintools)
library(testthat)

date()

test_dir("tests/")
```

### Code of Conduct

Please note that this project is released with a [Contributor Code of Conduct](CONDUCT.md). 
By participating in this project you agree to abide by its terms.
